\papertitle

### 2013-01-18 manuscript.tex
Remove millirobots from title
Swap H2Bird diagram with block diagram

%----------------------------------------------------------------------------%
% METADATA
\def \papertitle{Cooperative Control and Modeling for Narrow Passage Traversal with Millirobots}
\def \paperkeywords{AAMAS proceedings, multiagent systems, cooperative control, 
particle filter, micro air vehicle, ground station, visual servoing, pose 
estimation, flapping wing, ornithopter, biomimetic}
\def \paperterms{Algorithms, Performance, Design, Experimentation}
%\def \paperauthors{Ryan C. Julian, Cameron J. Rose, Humphrey Hu, and Ronald S. Fearing}
\def \paperauthors{Paper 580}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Robotic and Vision Platforms}
%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithopter}
% humphrey
To explore these cooperative control concepts, we designed a new 
flapping-wing MAV, known as the H$^2$Bird (Fig.~\ref{fig:h2bird}). Built 
around the Silverlit i-Bird RC flyer power train and clap-fling wings\footnote{\raggedright Silverlit Toys Manufactory Ltd.: i-Bird RC Flyer
\href{http://www.silverlit-flyingclub.com/wingsmaster/}
     {http://www.silverlit-flyingclub.com/wingsmaster/}}, 
the H$^2$Bird has a wingspan of 26.5 cm and a flight weight of 13 grams. A 
tail propeller and servo-controlled tail elevator provide control in the yaw 
and pitch axes (Fig.~\ref{fig:h2Bird_axes}). The on-board ImageProc 2.4\footnote{ImageProc 2.4: \\
\href{https://github.com/biomimetics/imageproc\_pcb}
     {https://github.com/biomimetics/imageproc\_pcb}} 
controller includes of a 40 MIPS microprocessor, 6 DOF IMU, 
IEEE 802.15.4 radio, VGA camera, and motor drivers, all powered by a 90 mAh 
lithium polymer battery. In routine flight, the H$^2$Bird averages 1.2 m/s 
ground speed, and operates for approximately 10 minutes.

%----------------------------------------------------------------------------%
\subsection{Ground Station Computer Vision Platform}
% ryan
Cooperative behavior is a promising strategy for autonomous navigation in 
unexplored and unstructured environments. However, to operate in these 
environments, a cooperative system must be fully mobile, not tied to a 
static ground station or motion capture laboratory. To demonstrate the 
feasibility of this approach, we designed our ground station to conform to 
the power and weight constraints of highly mobile millirobotic ground 
vehicles, such as OctoRoACH, which can traverse rough terrains with speed and 
agility~\cite{Pullin2012Dynamic}.

@@

Our ground station software is based on the Ubuntu Linux\footnote{\raggedright Ubuntu: 
Canonical Ltd., \href{http://www.ubuntu.com/}{http://www.ubuntu.com/}} distribution
modified with a custom version of the Linux kernel. 
We use the Python\footnote{\raggedright Python: Python Software Federation, \href{http://www.python.org/}
{http://www.python.org/}} programming language for control, robot 
communication, and telemetry, and the OpenCV\footnote{\raggedright OpenCV: Willow Garage, 
\href{http://opencv.willowgarage.com/wiki/}{http://opencv.willowgarage.com/wiki/}} 
computer vision libraries for image capture and processing.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Concept and Algorithms}
%TODO ryan

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/process_flow.pdf}
\caption{Overview of the cooperative control system.}
\label{fig:process_flow}
\end{figure}
%TODO h2bird label in diagram should have superscript

@@

\begin{figure}[!tb]
\centering
\includegraphics[height=150pt]{figures/h2bird_axes.pdf}
\caption{H$^2$Bird ornithopter with attitude control axes and labeled 
control surfaces.}
\label{fig:h2Bird_axes}
\end{figure}
%TODO label h2bird drawing

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments, Results, and Performance}
\label{sec:performance}
%TODO cameron
To bound the performance of the cooperative control system, we determine 
the feasible set of initial conditions that result in successful narrow 
passage traversal, using both analytical and empirical methods. We then 
conduct experiments to validate this model.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/step_response_total.pdf}
\caption{H$^2$Bird step response}
\label{fig:step_response}
\end{figure}
%TODO reduce number of sig figs

@@

\begin{figure*}[tb]
\begin{minipage}[t]{0.45\linewidth}
\includegraphics[width=\textwidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{minipage}
\hfill
\begin{minipage}[t]{0.47\linewidth}
\centering
\centering
\includegraphics[width=\textwidth]{figures/heat_map.pdf}
\caption{Probability of success for all starting locations. This graphic is 
a result of a Monte Carlo simulation of the reachable set model, in which the 
initial heading of the H$^2$Bird is chosen uniformly at random from $(-90^{\circ},90^{\circ})$.}
\label{fig:heat_map}
\end{minipage}
\end{figure*}

>>>>

%----------------------------------------------------------------------------%
% METADATA
\def \papertitle{Cooperative Control and Modeling for Narrow Passage Traversal}
\def \paperkeywords{AAMAS proceedings, multiagent systems, cooperative control, 
particle filter, micro air vehicle, ground station, visual servoing, pose 
estimation, flapping wing, ornithopter, biomimetic}
\def \paperterms{Algorithms, Performance, Design, Experimentation}
%\def \paperauthors{Ryan C. Julian, Cameron J. Rose, Humphrey Hu, and Ronald S. Fearing}
\def \paperauthors{Paper 580}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Robotic and Vision Platforms}
%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithopter}

\begin{figure}[!tb]
\centering
\includegraphics[height=150pt]{figures/h2bird_axes.pdf}
\caption{H$^2$Bird ornithopter with attitude control axes and labeled 
control surfaces.}
\label{fig:h2Bird_axes}
\end{figure}

To explore these cooperative control concepts, we designed a new 
flapping-wing MAV, known as the H$^2$Bird (Fig.~\ref{fig:h2bird}). Built 
around the Silverlit i-Bird RC flyer power train and clap-fling wings\footnote{\raggedright Silverlit Toys Manufactory Ltd.: i-Bird RC Flyer
\href{http://www.silverlit-flyingclub.com/wingsmaster/}
     {http://www.silverlit-flyingclub.com/wingsmaster/}}, 
the H$^2$Bird has a wingspan of 26.5 cm and a flight weight of 13 grams. A 
tail propeller and servo-controlled tail elevator provide control in the yaw 
and pitch axes (Fig.~\ref{fig:h2Bird_axes}). The on-board ImageProc 2.4\footnote{ImageProc 2.4: \\
\href{https://github.com/biomimetics/imageproc\_pcb}
     {https://github.com/biomimetics/imageproc\_pcb}} 
controller includes of a 40 MIPS microprocessor, 6 DOF IMU, 
IEEE 802.15.4 radio, VGA camera, and motor drivers, all powered by a 90 mAh 
lithium polymer battery. In routine flight, the H$^2$Bird averages 1.2 m/s 
ground speed, and operates for approximately 10 minutes.

%----------------------------------------------------------------------------%
\subsection{Ground Station Computer Vision Platform}
Cooperative behavior is a promising strategy for autonomous navigation in 
unexplored and unstructured environments. However, to operate in these 
environments, a cooperative system must be fully mobile, not tied to a 
static ground station or motion capture laboratory. To demonstrate the 
feasibility of this approach, we designed our ground station to conform to 
the power and weight constraints of highly mobile millirobotic ground 
vehicles, such as OctoRoACH, which can traverse rough terrains with speed and 
agility~\cite{Pullin2012Dynamic}.

@@

Our ground station software is based on the Ubuntu Linux\footnote{\raggedright Ubuntu: 
Canonical Ltd., \href{http://www.ubuntu.com/}{http://www.ubuntu.com/}} distribution
modified with a custom version of the Linux kernel. 
We use the Python\footnote{\raggedright Python: Python Software Federation, \href{http://www.python.org/}
{http://www.python.org/}} programming language for control, robot 
communication, and telemetry, and the OpenCV\footnote{\raggedright OpenCV: Willow Garage, 
\href{http://opencv.willowgarage.com/wiki/}{http://opencv.willowgarage.com/wiki/}} 
computer vision libraries for image capture and processing.
%TODO mention code is open source, available on GitHub

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Concept and Algorithms}

@@

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/process_flow.pdf}
\caption{Overview of the cooperative control system.}
\label{fig:process_flow}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments, Results, and Performance}
\label{sec:performance}
To bound the performance of the cooperative control system, we determine 
the feasible set of initial conditions that result in successful narrow 
passage traversal, using both analytical and empirical methods. We then 
conduct experiments to validate this model.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/step_response_total.pdf}
\caption{H$^2$Bird step response}
\label{fig:step_response}
\end{figure}

@@

\begin{figure*}[tb]
\begin{minipage}[t]{0.45\linewidth}
\includegraphics[width=\textwidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{minipage}
\hfill
\begin{minipage}[t]{0.47\linewidth}
\centering
\centering
\includegraphics[width=\textwidth]{figures/heat_map.png}
\caption{Probability of success for all starting locations. This graphic is 
a result of a Monte Carlo simulation of the reachable set model, in which the 
initial heading of the H$^2$Bird is chosen uniformly at random from $(-90^{\circ},90^{\circ})$.}
\label{fig:heat_map}
\end{minipage}
\end{figure*}
